Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-04 lineages_18Q3.Rmd

```{r, eval=FALSE}
crispr_signif_lvlA_lineage <- readRDS("./data_munging/rds/crispr_signif_lvlA_lineage.rds")

@@

```{r fig.height=5, fig.width=20}
genes_lvlA_filt <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent

@@

crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  guides(color = FALSE) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 5, units = "in")

crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  coord_cartesian(ylim = c(-2, 2)) +
  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted_truncated
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
```

@@

lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 1, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = lvlA_signif_color) + 
  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES scores for significant Level A G2P genes",
       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
lvlA_signif_genes_plot

>>>>

```{r, eval=TRUE}
crispr_signif_lvlA_lineage <- readRDS("./data_munging/rds/crispr_signif_lvlA_lineage.rds")

@@

```{r fig.height=4, fig.width=20}
genes_lvlA_filt <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent

@@

crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  guides(color = FALSE) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 4, units = "in")

crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  coord_cartesian(ylim = c(-2, 2)) +
  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted_truncated
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 4, units = "in")
```

@@

lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 1, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = lvlA_genes_signif_color) + 
  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES scores for significant Level A G2P genes",
       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
lvlA_signif_genes_plot
